### 2019-02-21 sections/semantics.tex
small fixes and more fixmes
shuffle around pars for readability

\TOPHAT is designed such that a user interface can be generated from a task's syntax tree.
A possible graphical user interface is shown in \cref{fig:flight-booking}, where tasks are rendered as \HTML pages.
Editors are rendered as input fields,
external choices are represented by two buttons,
and parallel tasks are rendered side by side.
Steps only show the interface of their left hand side.
In case of an external step they are accompanied by a button.
When the guard condition of a step is not fulfilled, the button is disabled.

@@

Inputs $i$ are formed according to the grammar in \cref{fig:input-grammar}.
Handling input is done by the \emph{handling} semantics shown in \cref{fig:handling-semantics}.
It is a small step semantics with labelled transitions.
It takes a task $t$ in a state $s$ and an input $i$, and yields a new task $t'$ in a new state $s'$.

@@

@@

\refrule{H-Change},
\refrule{H-Empty},
\refrule{H-Fill},
\refrule{H-Update}:
Input events $v$ and $\Empty$ are used to change the value of editors and empty them.
Editors only accept values of the correct type.

@@

There is a function $\Inputs$ which calculates the possible input events a given task expects.
It takes a normalised task and a state and returns a set of inputs that can be handled.
The definition of this function is listed in \cref{fig:observation-input}.

@@

The semantics have been implemented in the Idris programming language \cite{journals/jfp/Brady13}.
We use techniques presented by \textcite{journals/entcs/JaskelioffGH11}, \textcite{journals/jfp/Swierstra08}, and \textcite{school/maktoberdorf/PeytonJones01}.
Such an implementation increases the confidence in the correctness and completeness of the semantics.
The source code can be found on GitHub.\footnote{\url{http://github.com/XXX/XXX}}
A proof of concept implementation in Haskell is also available, showing that \TOPHAT can be implemented without dependent types.

A command-line interface is part of this implementation.
It prompts users to type input events, which get parsed and processed by the interaction semantics.

>>>>

\fixme{Add $\UserInterface$ to appendix and refer.}
\TOPHAT is designed such that a user interface can be generated from a task's syntax tree.
A possible graphical user interface is shown in \cref{fig:flight-booking}, where tasks are rendered as \HTML pages.
Editors are rendered as input fields,
external choices are represented by two buttons,
and parallel tasks are rendered side by side.
Steps only show the interface of their left hand side.
In case of an external step they are accompanied by a button.
When the guard condition of a step is not fulfilled, the button is disabled.

@@

Inputs $i$ are formed according to the grammar in \cref{fig:input-grammar}.
%
There is a function $\Inputs$ which calculates the possible input events a given task expects.
It takes a normalised task and a state and returns a set of inputs that can be handled.
The definition of this function is listed in \cref{fig:observation-input}.

@@

Handling input is done by the \emph{handling} semantics shown in \cref{fig:handling-semantics}.
It is a small step semantics with labelled transitions.
It takes a task $t$ in a state $s$ and an input $i$, and yields a new task $t'$ in a new state $s'$.

@@

%FIXME: Revert rule names in front to normal sentences?
\refrule{H-Change},
\refrule{H-Empty},
\refrule{H-Fill},
\refrule{H-Update}:
Input events $v$ and $\Empty$ are used to change the value of editors and empty them.
Editors only accept values of the correct type.

@@

@@

The semantics have been implemented in the Idris programming language \cite{journals/jfp/Brady13}.
We use techniques presented by \textcite{journals/entcs/JaskelioffGH11}, \textcite{journals/jfp/Swierstra08}, and \textcite{school/maktoberdorf/PeytonJones01}.
% Such an implementation increases the confidence in the correctness and completeness of the semantics.
The source code can be found on GitHub.\footnote{\url{http://github.com/XXX/XXX}}
% A proof of concept implementation in Haskell is also available, showing that \TOPHAT can be implemented without dependent types.
A command-line interface is part of this implementation.
It prompts users to type input events, which get parsed and processed by the interaction semantics.

Also, we mad an implementation of \TOPHAT combinators into \ITASKS,
so that \TOPHAT specifications can be compiled to runnable applications.
This shows that \TOPHAT is a subset of \ITASKS.
